External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-11-05 CVPR2017_Review_Unified.tex
add

%%%%%%%%% ABSTRACT
\begin{abstract}
Image priors (e.g., sparsity, self-similarity) are playing key roles in image denoising problem. External priors are priors learned from external (usually clean) images while internal priors are learned from the given noisy image. The external priors are more generative on recovering structures in images while the internal priors are more adaptive on recovering textures and details in given noisy image. In this paper, we propose an algorithm of external priors guided internal priors learning for real image denoising. Specifically, the external priors are learned on patch groups (PGs) from external images via Gaussian Mixture Model, and employed to guide the clustering and orthogonal dictionary learning of PGs from the given noisy image. The orthogonal dictionary learning has closed-form solutions and the image denoising is simultaneously performed with the learning process. We perform extensive experiments on real image denoising, in which the noisy images are captured by different cameras and camera settings under controlled indoor or uncontrolled outdoor lighting conditions. The results on PSNR and visual quality demonstrate that the proposed method achieves better performance than other state-of-the-art denoising methods. 
\end{abstract}
%Though these methods are very effective in Gaussian noise removal, the noise in real images are signal dependent and more complex than Gaussian noise. Therefore, only exploiting the external or internal priors are not enough for real image denoising.

@@

Most vision systems, such as medical imaging and surveillance, need accurate feature extraction from high-quality images. The camera sensors and outdoor low light conditions will unavoidably bring noise to the captured images. The impact is that the image details will be lost or hardly visible. As a result, image denoising is an essential procedure for the reliability of these vision systems. In the research area, image denoising is also an ideal platform for testing natural image models and provides high-quality images for other computer vision tasks such as image registration, segmentation, and pattern recognition.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Image priors (e.g., sparsity, self-similarity) are playing key roles in image restoration problems such as denoising. External priors are priors learned from external (usually clean) images while internal priors are learned from the given noisy image. The external priors are more generative on recovering structures in images while the internal priors are more adaptive on recovering textures and details in given noisy image. In this paper, we propose an algorithm of external priors guided internal priors learning for real image denoising. Specifically, the external priors are learned on patch groups (PGs) from external images via Gaussian Mixture Model, and employed to guide the clustering and orthogonal dictionary learning of PGs from the given noisy image. The orthogonal dictionary learning has closed-form solutions and the image denoising is simultaneously performed with the learning process. We perform extensive experiments on real image denoising, in which the noisy images are captured by different cameras and camera settings under controlled indoor or uncontrolled outdoor lighting conditions. The results on PSNR and visual quality demonstrate that the proposed method achieves better performance than other state-of-the-art denoising methods. 
\end{abstract}
%Though these methods are very effective in Gaussian noise removal, the noise in real images are signal dependent and more complex than Gaussian noise. Therefore, only exploiting the external or internal priors are not enough for real image denoising.

@@

Most vision systems, such as medical imaging and surveillance, need accurate feature extraction from high-quality images. The camera sensors and outdoor low light conditions will unavoidably bring noise to the captured images. The impact is that the image details will be lost or hardly visible. As a result, image denoising is an essential procedure for the reliability of these vision systems. In the research area, image denoising is an ideal platform for testing natural image models and provides high-quality images for other computer vision tasks such as image registration, segmentation, and pattern recognition.
